### 2024-01-14 Paper/main.tex
fix figure
change resNet to ResNet-18

\subsection{Evaluation of ResNet Performance Without Transfer Learning} 
Prior to the implementation of transfer learning methodologies, an analysis was conducted to ascertain whether the selected ResNet architecture could independently identify various image compression algorithms. The entire dataset of one specific compression size, was processed through the model, and the outputs were L2 normalized. This resulted in 1000 dimension vectors for each image.

@@

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{Plots/plot_scatter_without_transfer_10.pgf}
	\caption{10kB Compression: ResNet without transfer learning}
	\label{fig: no_transfer}
\end{figure}

>>>>

\subsection{Evaluation of ResNet-18 Performance Without Transfer Learning} 
Prior to the implementation of transfer learning methodologies, an analysis was conducted to ascertain whether the ResNet-18 architecture could independently identify various image compression algorithms. The entire dataset of one specific compression size, was processed through the model, and the outputs were L2 normalized. This resulted in 1000 dimension vectors for each image.

@@

\begin{figure}[h!]
	\centering
	\resizebox{\textwidth}{!}{\input{../Plots/plot_scatter_without_transfer_10.pgf}}
    \caption{Archived filesizes for used encoder}
	\label{fig: no_transfer}
\end{figure}
